cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-16 paper-cardinalR.Rmd
Updated application projections

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.9, 
                                              axis_pos_y = -0.9, 
                                              threshold = 0.07))

@@

five_clusts_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.1, 1.2), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")
```

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.9, 
                                              axis_pos_y = -0.9, 
                                              threshold = 0.05))

@@

five_clusts_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.1, 1.1), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.9, 
                                              axis_pos_y = -0.9, 
                                              threshold = 0.05))

@@

five_clusts_proj1_1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.1, 1), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")

@@

five_clusts_proj2_1 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.1, 1.2), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")
```

@@

five_clusts_proj3_1 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.1, 1.1), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")

@@

five_clusts_proj1_2 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.1, 1), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")

@@

five_clusts_proj2_2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.1, 1.2), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")
```

@@

five_clusts_proj3_2 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.1, 1.1), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")

>>>>

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.55,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.4, 
                                              axis_pos_y = -0.4, 
                                              threshold = 0.05))

@@

five_clusts_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.5, 0.67), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")
```

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.5,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.35, 
                                              axis_pos_y = -0.35, 
                                              threshold = 0))

@@

five_clusts_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.45, 0.55), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")

@@

@@

five_clusts_proj1_1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.5, 0.5), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")

@@

five_clusts_proj2_1 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.5, 0.67), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")
```

@@

five_clusts_proj3_1 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.45, 0.55), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")

@@

five_clusts_proj1_2 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.5, 0.5), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")

@@

five_clusts_proj2_2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.5, 0.67), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")
```

@@

five_clusts_proj3_2 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.45, 0.55), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e')) +
  theme(legend.position = "none")
